\documentclass{article}
\usepackage{times}
\usepackage{fullpage}

\newcommand{\head}{\subsection*}
\setlength{\parindent}{0pt}

\begin{document}

%_______________________________________________________________________________
% Heading section
%_______________________________________________________________________________
\begin{center}
\rule{\textwidth}{1.5pt} \\ \rule[10pt]{\textwidth}{1pt}\\
CMU 17-651\hfill Models of Software Systems\\[3ex]
{\Large\bf Project 2: Concurrency}\\[3ex]
Garlan \& Kang \hfill {\bf Due: November 14, 2018} \rule{\textwidth}{1pt}
\\\rule[9.5pt]{\textwidth}{1.5pt}
\end{center}

The purpose of this second project is to give you experience in
modeling a realistic system as a state machine using concurrency.
The example that we will use is the familiar Infusion Pump.
A general description of an Infusion Pump and a variety of documents describing 
failures of real infusion pump systems can be found in the
Infusion Pump Documents Module on the class website. The key
ideas that we would like you to get out of this project are: (1) the
use of concurrency to manage complexity, separate concerns, model
reality; (2) checking of properties related to concurrency (safety
and liveness); and (3) additional practice in creating appropriately
abstract models.

\bigskip You should carry out this project in your assigned team. Make sure that everyone in the
group contributes to the overall effort. Each team should submit a single write-up of the project,
due at the beginning of class on the project due date. We have posted a template for a group
project write-up under the Latex section of the course web site.

\bigskip To give you a head start, we are including a very simple model of an infusion pump, which you may want to use as a starting point for your modeling effort. 

%___________________________________________________________________________________________________
\head{Task 1 (50 points): Modeling with Concurrency}
%___________________________________________________________________________________________________

Model a 2-line infusion pump in FSP, using concurrency to factor the model into parts that
represent different concerns. Possibilities for separation include things like (a) power system (b) an individual line (c) alarms (d) user interface for setting of the pump (both initially and during operation).

\bigskip

As always, you will need to pick a level of abstraction appropriate for this model, and it is up to
you to figure out what are the significant aspects of the system that should be included in your
model.

%___________________________________________________________________________________________________
\head{Task 2 (32 points): Stating and Checking Properties}
%___________________________________________________________________________________________________

Once you have your pump specified, consider the following properties. For each say (a) whether the property
is a safety or liveness property,  (b) whether your model allows you to check this property, and if
so, (c) whether it is true or not, and what features of FSP and LTSA allowed you to check the
property. It would be particularly helpful if you include in your write-up the specific checks that you performed -- which should also appear in your FSP file. (Note: not all of these properties have to be true of your pump, depending on how you interpret the requirements for an infusion pump.)

\begin{enumerate}
    \item The pump cannot start pumping without the operator first confirming the settings on the pump.
    \item Electrical power can fail at any time.
    \item If the backup battery power fails, pumping will not occur on any line.
    \item It is always possible to resume pumping after a failure.
    \item An alarm will sound on any line failure (blockage, pinching, empty fluid, or
whatever failures you model).
    \item In the absence of errors the pump will continue to pump until the
treatment is finished.
    \item The system never deadlocks.
    \item Property A of your choosing.
    \item Property B of your choosing
\end{enumerate}

%___________________________________________________________________________________________________
\head{Task 3 (18 points): Reflection}
%___________________________________________________________________________________________________

 You have now seen several notations for specifying systems and their properties: Pre-post conditions,
 Alloy, and FSP (LTSA).  In this part of the report we would like you to reflect on that experience.
 For each of these notations write a paragraph or two explaining:
\begin{enumerate}
 \item What are the strengths of this notation and its tools?  Under what situations would you
recommend its use? Why?
 \item What are the weaknesses of this notation and its tools. Under what
situations would you not recommend its use? Why?
 \item With respect to this notation, what is
the single most-important future development that would be needed to make it more generally useful
to practitioners?

\end{enumerate}

\end{document}
